---
title: "p8105_hw5_amh2325"
author: "Amanda Howarth"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(broom)
```

## Load IRIS dataset from the TIDYVERSE 
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```
## PROBLEM 1
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement. 

```{r}
iris_function1 = function(x) {
  if (is.numeric(x)) {
    replace_na(x, mean(x, na.rm = TRUE)) }
    
  else if(!is.numeric(x)) {
    replace_na(x, "virginica") }
}
```

```{r}
replace_iris = map(.x=iris_with_missing, ~iris_function1(.x)) %>% 
  as_tibble
replace_iris
```
## PROBLEM 2
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time. 
```{r}
treatment_study = list.files(path="./data/", full.names = TRUE)

treatment_study_data = 
  treatment_study %>%
  map_df(read.csv) %>% 
  mutate(
    "subject_id" = c(1:20),
    "treatment_arm" = c("control", "control", "control", "control", "control", "control", "control", "control", "control", "control", "experimental", "experimental", "experimental", "experimental", "experimental", "experimental", "experimental", "experimental", "experimental", "experimental")
  ) %>% 
  select("subject_id", "treatment_arm", everything())%>% 
  pivot_longer(
    week_1:week_8, 
    names_to = "week",
    values_to = "result"
  ) %>%
  mutate(week = recode(week, "week_1" = "1", "week_2" = "2", "week_3" = "3", "week_4" = "4", "week_5" = "5", "week_6" = "6", "week_7" = "7", "week_8" = "8"))

treatment_study_data
```
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups. 
```{r}
ggplot(treatment_study_data, aes(x = week, y = result, group = subject_id,
  color = treatment_arm)) + geom_point() + geom_line()
  
  labs(title = "Study Results for Subjects In Control and Experimental Groups, Over an 8-Week Study Period", 
           x = "Week",
           y = "Results") +
  theme(plot.title = element_text(size = 10, face = "bold"))
```
Overall, the subejcts in the control group experienced results (observations) of lower values each week (for all 8 weeks) compared to subjects in the experimental group. Thus, if the result was, for example, improved eyesight, it would appear that the treatment would have worked better for participants receiving treatment in the experimental group.

## PROBLEM 3 
 Set the following design elements:
 1) Fix n=30 <br>
 2) Fix xi1 as draws from a standard Normal distribution <br>
 3) Fix β0=2 <br>
 4) Fix σ2=50 <br>
 5) Set β1=0. Generate 10000 datasets from the model <br>
```{r}
set.seed(1)

sim_regression = function(n = 30, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sqrt(50)))
  
  ls_fit = lm(y ~ x, data = sim_data) %>%
    broom::tidy()
  
  tibble(
    beta1_hat = ls_fit[[2,2]],
    p_value = ls_fit[[2,5]])
}

sim_output = rerun(10000, sim_regression(beta1=0)) %>%
  bind_rows()
```

Repeat the above for β1={1,2,3,4,5,6}

```{r}
sim_results = 
  tibble(beta1_new = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(output_list = map(.x = beta1_new, ~rerun(10000, sim_regression(beta1 = .x))),
  estimate_df = map(output_list, bind_rows))%>%
  select(-output_list)%>% 
  unnest(estimate_df)
```
Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β1 on the x axis. Describe the association between effect size and power.

```{r}
sim_results %>% 
  mutate(null_rejected = ifelse(p_value < 0.05, "reject", "fail to reject")) %>% 
  group_by(beta1_new, null_rejected) %>% 
 summarise_(n= ~n()) %>%
  mutate(proportion = prop.table(n/sum(n))) %>% 
  filter(null_rejected == "reject") %>%
  ggplot(aes(x = beta1_new, y = proportion)) +  geom_line() +
  
  labs(title = "Power of Test per Effect Size (true value of beta1)", 
           x = "Effect Size",
           y = "Power") +
  theme(plot.title = element_text(size = 10, face = "bold"))
```
**Describe the association between effect size and power.**
We can see above that as the effect size increases, power also increases. 


1) Make 1st plot showing the average estimate of β̂ 1 on the y axis and the true value of β1 on the x axis. <br>
2) Make 2nd second plot the average estimate of β̂ 1 only in samples for which the null was rejected on the y axis and the true value of β1 on the x axis
```{r}
plot1 = sim_results %>% 
  group_by(beta1_new) %>% 
  summarise(mean_beta_hat = mean(beta1_hat)) %>% 
    ggplot(aes(x = beta1_new, y = mean_beta_hat)) + geom_point() +geom_line() +
  
  labs(title = "Average Beta1_hat values Across True Values of Beta1", 
           x = "True Values of Beta1",
           y = "Average Values of Beta1_hat") +
  theme(plot.title = element_text(size = 10, face = "bold"))
plot1

plot2 = sim_results %>% 
  mutate(null_rejected = ifelse(p_value < 0.05, "reject", "fail to reject")) %>% 
  group_by(beta1_new, null_rejected) %>% 
  filter(null_rejected == "reject") %>%
  summarise(mean_beta_hat = mean(beta1_hat)) %>% 
    ggplot(aes(x = beta1_new, y = mean_beta_hat)) + geom_point() +geom_line() +
  
  labs(title = "Average Beta1_hat values Across True Values of Beta1, when the Null is Rejected (p-value < 0.05)", 
           x = "True Values of Beta1",
           y = "Average Values of Beta1_hat (Null is Rejected") +
  theme(plot.title = element_text(size = 10, face = "bold"))
plot2
```

**Is the sample average of β̂ 1 across tests for which the null is rejected approximately equal to the true value of β1? Why or why not?**

One can see above that the sample average of β̂1 across tests for which the null is rejected is NOT approximately equal to the true value of β1. The average values of β̂1 are overall higher for the true value of β1 when the null is rejected compared to the total sample (rejected and failed to reject), where the sample average of β̂1 across tests IS approximately equal to the true value of β1. However, when comparing the plots, they are similar when the true value of  β1 = 0 and when the true value of β1 approaches 6. 

12